---
title: "Example Analysis"
bibliography: references.bib
---

# Background

According to the 2020 United States Census, 8.5% of households did not have a vehicle, 32.5% had at least one vehicle, and 37.1% had at least two "vehicles available" [@census]. Jurisdctions with the lowest car ownership were Washington, D.C., New York, and Massachusetts [@timmons]. 

```{r}
#| echo: false
#| fig-align: center
#| fig-cap: "Fig 1: Map of car ownership rates by household. Source: Matt Timmons"
#| fig-cap-location: margin
knitr::include_graphics("https://res.cloudinary.com/value-penguin/image/upload/c_limit,dpr_1.0,f_auto,h_1600,q_auto,w_1600/v1/car-ownership_ulmhvi")
```

This analysis is directed at those in the market for a used vehicle. It aims to answer the question what influences a vehicles miles per gallon (MPG).

    
# Data
The data used in this analysis is Motor Trend Car Road Tests (mtcars), which comes pre-installed with R. It contains information on 32 vehicles across 11 variables. All variables are numeric.
```{r}
install.packages("tidyverse")
load("tidyverse")
data(mtcars)
data_dict <- tibble(
    "Cariable" = c("mpg", "cyl", "disp", "hp", "drat", "wt", "qsec", "vs", "am", "gear", "carb"),
    "Name" = c("Miles per US gallon", "Number of cylinders", "Displacement (cu.in.)", "Gross horsepower", "Rear axle ratio", "Weight (1000 lbs)", "1/4 mile time", "Engine (0 = V-shaped, 1 = straight)", "Transmission (0 = automatic, 1 = manual)", "Number of forward gears", "Number of carburetors")
    )

knitr::kable(data_dict)
```

:::{.callout-note}
Data dictionary
Variable        Name
--------        -----
mpg             Miles per US gallon

cyl             Number of cylinders

disp            Displacement (cu.in.)

hp              Gross horsepower

drat            Rear axle ratio

wt              Weight (1000 lbs)

qsec            1/4 mile time

vs              Engine (0 = V-shaped, 1 = straight)

am              Transmission (0 = automatic, 1 = manual)

gear            Number of forward gears

carb            Number of carburetors

[@mtcars]
:::
    
# Data wrangling
Your analysis must include some minimal form of data wrangling with you using at least five different functions from `dplyr` or `tidyr`. 
    
# Plots
- Your analysis should include at least three plots with you using at least three different `geom_*()` functions from `ggplot2` (or another package with `geom_*()` functions). 
- Plots should have titles, subtitles, captions, and human-understandable axis labels. 
- At least one plot should using a type of faceting (`facet_grid()` or `facet_wrap()`). 

    
# Callout blocks
Your analysis must include at least two different [callout blocks](https://quarto.org/docs/authoring/callouts.html).
    
# Margin Content
Your analysis must include the use of at least 1 [margin content](https://www.stephaniehicks.com/jhustatprogramming2022/posts/2022-10-27-build-website/#margin-content). 
    
# Summary
You must summarize your analysis and/or results with a paragraph (4-6 sentences).
    
# Functions used
At the end of the data analysis, list out each of the functions you used from each of the packages (`dplyr`, `tidyr`, and `ggplot2`) to help the TA with respect to making sure you met all the requirements described above. 

dplyr or tidyr:
1.
2.
3.
4.
5.


ggplot2:
1.
2.
3.




